### 2025-02-23 paper/relatedwork.tex
Spacefiller for DML.

\paragraph{Typed rank polymorphism}
Gibbons showed how to express a form of rank polymorphism in Haskell,
through the use of \emph{Naperian
  functors}~\cite{10.1145/2976022.2976023}. This form of rank
polymorphism is somewhat more limited than ours; in particular, it
imposes static ranks. Further, Gibbons' work focused solely on the
embedding in Haskell, while our system also supports code extraction
and demonstrates good real-world performance.

>>>>

\paragraph{Type systems}
Verifying array indexing is a common application of dependent
types, as seen in for example Dependent ML~\cite{10.1145/292540.292560}.

Gibbons showed how to express a form of rank polymorphism in Haskell,
through the use of \emph{Naperian
  functors}~\cite{10.1145/2976022.2976023}. This form of rank
polymorphism is somewhat more limited than ours; in particular, it
imposes static ranks. Further, Gibbons' work focused solely on the
embedding in Haskell, while our system also supports code extraction
and demonstrates good real-world performance.
